%% Dr. Vinny Gupta - Curriculum Vitae

\documentclass[12pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) so accented characters are a single glyph
\usepackage[utf8]{inputenc} % allow input of utf-8 encoded characters
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % automatically regionalize hyphens, quote marks, etc
\usepackage{microtype} % improves text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto} % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts

% what is your name?\newcommand{\myname}{Vinny Gupta}

% define a default font face and set it as the body font
\usepackage{crimson} % document's serif font
\usepackage{helvet}  % document's sans serif font

% define how far to tab for list items with left-aligned date - different font faces need different widths
\newcommand{\listtabwidth}{1.75cm}

% set name font to title the document
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*}{20}
\titleformat{\section}{\sffamily\small\bfseries\lsstyle\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{24pt plus 4pt minus 2pt}{12pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{12pt plus 4pt minus 2pt}{8pt plus 2pt minus 2pt}

% set page margins
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=0.8in}

% prevent paragraph indentation
\setlength\parindent{0em}

% define space between list items
\newcommand{\listitemspace}{0.15em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
            \setlength{\parskip}{0em}
            \setlength{\itemsep}{\listitemspace}
            \setlength{\parsep}{\listitemspace}}}
    {\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print the month and year only when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    pdfauthor   = {Vinny Gupta},
 %   pdfkeywords = {city planning, housing, street networks, transportation, urban design, urban informatics},
    pdftitle    = {Vinny Gupta: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\pagestyle{empty}

\begin{document}
    \raggedright

    % display name as the document title
    \namefont{Vinny Gupta}

    % affiliation and contact info blocks
    \vspace{1em}
    \begin{minipage}[t]{0.700\textwidth}
        % current primary affiliation, left-aligned
		Department of Mechanical and Mechatronics Engineering	\\        
        Faculty of Engineering \\
        University of Waterloo
    \end{minipage}
    \begin{minipage}[t]{0.295\textwidth}
        % contact info details, right-aligned
        \flushright{}
        \href{mailto:vinny.gupta@uwaterloo.ca}{vinny.gupta@uwaterloo.ca} \\
        +(1) 226-606-0484 \\
        \href{https://orcid.org/0000-0003-0514-5834}{0000-0003-0514-5834}
    \end{minipage}

%  % contact info
%\vspace{1em}
%\begin{minipage}[t]{0.4\textwidth}
%Email: \href{mailto:vinny.gupta@sydney.edu.au}{vinny.gupta@sydney.edu.au} \\
%Phone: +(61) 424 032 837 \\
%  ORCID: \href{https://orcid.org/0000-0003-0514-5834}{0000-0003-0514-5834} \\
%% \href{https://scholar.google.com/citations?user=OHVguZIAAAAJ&hl=en}{Google Scholar}
%\end{minipage}
%\vspace{0.5em}

   % \section*{Research Interests}
    
%	experimental combustion, fire dynamics, laser diagnostics, fire suppression, fluid mechanics, and heat transfer 	
	    \section*{Education}

    \begin{tablist}

        \item[PhD] \tab{}Fire Safety Engineering, The University of Queensland, 2021
        \\ Thesis: \textit{Open-plan compartment fire dynamics}
        \\ Supervisor: Dr. Juan P. Hidalgo \\
        
        \item[BEng]  \tab{}Mechanical Engineering, The University of Queensland, 2015
        \\ Thesis: \textit{Evaluation of material flammability: Spacecraft fire safety experiment}
        \\ Supervisor: Prof. Jos\'{e} L. Torero

    \end{tablist}

    \section*{Appointments}

    \begin{tablist}

        \item[2024--] \tab \textbf{Assistant Professor} \\
                          University of Waterloo, Canada \\
 
        \item[2021--24] \tab \textbf{Research Associate} \\
                          The University of Sydney, Australia \\

		\item[2022--23] \tab \textbf{Lecturer in Fire Safety Engineering} (0.2 FTE) \\
                          The University of Queensland, Australia \\	

        \item[2018--19] \tab \textbf{Research Assistant} \\
                          UQ Fire Consultancy, Australia \\
 
        \item[2018--18] \tab \textbf{Visiting Researcher} \\
                           Research Institutes of Sweden (RISE), Sweden   \\

    \end{tablist}

\section*{Grant Funding}

\begin{tablist}

    \item[2025--29] \tab \textbf{Canadian Innovation Fund - John R. Evans Leaders Fund (CFI-JELF)} \newline
    \textit{Fast spectral imaging of fire emissions} \newline
    \textbf{CAD \$120,000} (100\% share) \newline
    Principal Investigator  

    \item[2025--29] \tab \textbf{National Sciences and Engineering Research Council (NSERC): Discovery} \newline
    \textit{Fire and explosion dynamics in Li-ion battery storage} \newline
    \textbf{CAD \$202,500} (100\% share) \newline
    Principal Investigator  

    \item[2025--26] \tab \textbf{NSERC General Research Fund: Equipment Upgrade and Repair (GRF-RERUR)} \newline
    \textit{Thermal imaging of fires} \newline
    \textbf{CAD \$10,000} (100\% share) \newline
    Principal Investigator        

    \item[2024--27] \tab \textbf{NSERC Alliance: Next Generation Wood Construction} \newline
    \textit{Quantifying the external flaming risk from mass timber compartments} \newline
    \textbf{CAD \$56,000} (100\% share) \newline
    Principal Investigator  

    \item[2024--25] \tab \textbf{Society of Fire Safety (Engineers Australia)} \newline
    \textit{Evaluating the ignition and jet flaming hazard of Li-ion cells in thermal runaway} \newline
    \textbf{AUD \$5,000} (100\% share) \newline
    Principal Investigator  

    \item[2023--24] \tab \textbf{Halliwell: Microgrant} \newline
    \textit{Auto-ignition and propagation of jet flames ejected from lithium-ion battery cells during thermal runaway} \newline
    \textbf{NZD \$2,500} (100\% share) \newline
    Principal Investigator

    \item[2022--22] \tab \textbf{Alicat Scientific: Merit Grant} \newline
    \textbf{USD \$2,000} (100\% share) \newline
    Principal Investigator  

\end{tablist}

    \section*{Awards} % to-do --> needs to be truncated down

    \begin{tablist}

        \item[2025] \tab \textbf{Distinguished Paper Award}, Combustion Institute. Best paper in \enquote{Fire Research} presented at the 40th International Symposium on Combustion. 
                    
        \item[2021] \tab \textbf{Sheldon Tieszen Student Award}, International Forum of Fire Research Directors. Best student-led paper at the 13\textsuperscript{th} International Symposium on Fire Safety Science. 

        \item[2019] \tab \textbf{Best Poster Prize}, 1\textsuperscript{st} Asia-Pacific Combustion Institute Summer School in Valparaiso, Chile. 
       
    \end{tablist} 

    \section*{Teaching Experience}

	\subsection*{Program Management}   

        \begin{tablist}
        
        \item{2025--} \tab Co-director of the University of Waterloo Fire Safety Engineering MEng program.
        
        \end{tablist}

    	\subsection*{Course Instruction}   
   
    \begin{tablist}

        \item[2025--] \tab Course coordinator, Fire Safety Engineering (ME 567, undergraduate) at University of Waterloo.
        
        \item[2025--] \tab Course coordinator, Fire Dynamics (ME 671, postgraduate). University of Waterloo.
        
        \item[2024--] \tab Course coordinator, Ordinary Differential Equations (ME 203, undergraduate). University of Waterloo.
        
    	\item[2022--23] \tab Course coordinator (part-time), Fire Dynamics (FIRE 7620, postgraduate). The University of Queensland.    	
                        
	\end{tablist} 	
    
    \section*{Service}

    \subsection*{Scientific}
    
    \begin{tablist}

    	\item[2024--26] \tab \textbf{Early Career Committee Co-Chair}, 15th International Symposium on Fire Safety Science

        \item[2024--26] \tab \textbf{Guest Editor}, Applications in Energy and Combustion Science

    	\item[2024--24] \tab \textbf{Session Chair}, 40th International Symposium on Combustion

    	\item[2023--23] \tab \textbf{Technical Committee Member}, 2023 Australian Combustion Symposium
        
       	\item[2022--23] \tab \textbf{Workshop Chair}, 13th International Symposium on Fire Safety Science
        
        \item[2020--] \tab \textbf{Journal Reviewer}, \textit{Proceedings of the Combustion Institute}, \textit{Fire Safety Journal}, \textit{Applications in Energy and Combustion Science}, \textit{Fire Technology}, \textit{Combustion Science and Technology}, \textit{Combustion and Flame}, \textit{Frontiers in Mechanical Engineering}, \textit{Applied Thermal Engineering}  

    	\item[2018--21] \tab \textbf{Vice President}, UQ Society of Fire Protection Engineers Student Chapter



    \end{tablist}	

    \subsection*{Professional Membership}

    \begin{tablist}

        \item[2019--] \tab Combustion Institute, Australia \& New Zealand (ANZ) Section
        \item[2019--] \tab International Association for Fire Safety Science
        \item[2015--] \tab Society of Fire Protection Engineers
        
    \end{tablist}
   
    \section*{Publications}

	\nocite{*}    


    	

    \section*{Conference Activity}

    \subsection*{Invited keynotes and presentations}
	
	\begin{tablist}

    \item[2025] \tab \textbf{\enquote{Laboratory experiments investigating thermal runaway of lithium-ion battery cells}}, Conexus Nuclear Fire Protection Peer Group Meeting, Chalk River, Canada. October. 

    \item[2023] \tab \textbf{\enquote{Self-extinction framework in large timber compartment fires}}, Institute of Fire Engineers Annual Conference 2023, Brisbane, Australia. August. 

    \item[2023] \tab \textbf{\enquote{Understanding the scales of building fires}}, FM Global, Norwood, United States of America. March. 
 
	\item[2022] \tab \textbf{\enquote{Fire dynamics and suppression in modern buildings}}, Danish Institute of Fire and Security Technology, Copenhagen, Denmark. June. 
	
	\item[2022] \tab \textbf{\enquote{Fire safety research at The University of Queensland}}, Imperial College London, London, Australia. June. 
 
	\item[2021] \tab \textbf{\enquote{Understanding the different scales of compartment fires}}, University of Maryland, Washington DC, USA. October. 

    \item[2019] \tab \textbf{\enquote{The challenges of prescribing an appropriate design fire for the structurally safe design of contemporary architecture}}, Institute of Fire Engineers Annual Conference, Melbourne, Australia. August.
	
	\end{tablist}
    
\subsection*{Conference Presentations}

 Asterisk* indicates paper published in Peer-Reviewed Journals or Proceedings above. \bigskip

    \begin{tablist}
         \item[2025] \tab \textbf{V. Gupta}, A.R.W. Macfarlane, M.J. Dunn, A. Alsewailem, T. Xiao, J. Subburaj, A. Farooq, A.R. Masri. \textbf{\enquote{\textbf{High-speed spectral imaging of Li-ion cell thermal runaway}}}. 4th International Symposium on Lithium Battery Fire Safety, Hong Kong. Oct. 30 -- Nov 2.

         \item[2025] \tab A. Alsewailem, J. Subburaj, A. Elkhazraji, M. Sy, \textbf{V. Gupta}, M.J. Dunn, A.R. Masri, A. Farooq, A. \textbf{\enquote{\textbf{A laser-based HF sensor for early warning of thermal runaway in Li-ion batteries}}}. 4th International Symposium on Lithium Battery Fire Safety, Hong Kong. Oc

         \item[2025] \tab B. Southern, \textbf{V. Gupta}, A.R.W. Macfarlane, M.J. Dunn, A. Alsewailem, T. Xiao, J. Subburaj, A. Farooq, A.R. Masri. \textbf{\enquote{\textbf{High resolution time evolution of ejecta ignition and propagation in LCO and NMC 18650 Li-ion cells}}}. 4th International Symposium on Lithium Battery Fire Safety, Hong Kong. Oct. 30 -- Nov 2.

         \item[2025] \tab \textbf{V. Gupta}, A.R.W. Macfarlane, M.J. Dunn, A. Alsewailem, T. Xiao, J. Subburaj, A. Farooq, A.R. Masri. \textbf{\enquote{\textbf{Revealing ignition modes of Li-ion battery cells in thermal runaway with joint high-speed imaging}}}. 15th Asia-Pacific Conference on Combustion, Singapore. May. 18 -- 22.

         \item[2025] \tab J. Dabrowski, \textbf{V. Gupta}, E.J. Weckman. \textbf{\enquote{\textbf{A medium-scale mass timber compartment fire experimental set-up and preliminary results testing ventilation}}}. 2nd NextGen Wood Conference 2025, Ottawa, Canada. May. 28 -- 30.

        \item[2024] \tab T. Xiao, \textbf{*V. Gupta}, M.J. Dunn, A.R. Masri. \textbf{\enquote{\textbf{Joint OH-PLIF and Mie scattering imaging of enhanced water mist suppression of buoyant fires}}}. Combustion Institute's 40th International Symposium - Emphasizing Energy Transition, Milan, Italy. Jul. 21 -- 26.

        \item[2023] \tab \textbf{V. Gupta}, T. Xiao, M. Dunn, J.L. Torero, A.R. Masri. \textbf{\enquote{\textbf{Temperature and mixture fraction imaging in a vertical wall fire}}}. 2023 Australian Combustion Symposium, Darwin, Australia. Nov. 26 -- 29.

        \item[2023] \tab \textbf{V. Gupta}, M. Dunn, C. Avila Jiminez, A.R.W. Macfarlane, S. Galindo Lopez, A.R. Masri. \textbf{\enquote{\textbf{Venting of 18650 lithium-ion batteries during thermal runaway}}}. 2023 Australian Combustion Symposium, Darwin, Australia. Nov. 26 -- 29.

        \item[2023] \tab *\textbf{V. Gupta}, T. Xiao, M. Dunn, J.L. Torero, A.R. Masri. \textbf{\enquote{\textbf{Leading edge stabilisation of vertical boundary layer diffusion flames}}}. 13\textsuperscript{th} International Symposium on Fire Safety Science, Tsukuba, Japan. Oct 22--27.
        
        \item[2023] \tab \textbf{V. Gupta}, T. Xiao, M. Dunn, A.R. Masri. \textbf{\enquote{\textbf{Structure of the Sydney buoyant fire burner with varying levels of fuel-turbulence}}}. 12\textsuperscript{th} FM Global Open Source CFD Fire Modelling Workshop, Norwood, United States of America, Apr 4--5.

        \item[2023] \tab *\textbf{V. Gupta}, T. Xiao, M. Dunn, J.L. Torero, A.R. Masri. \textbf{\enquote{\textbf{Blowoff at the leading edge of a vertical boundary layer diffusion flame established over a porous 3D printed burner}}}. 12\textsuperscript{th} Mediterranean Combustion Symposium, Luxor, Egypt. Jan 23--26.

    	\item[2021] \tab *\textbf{V. Gupta}, J.P. Hidalgo, A. Cowlard, C. Abecassis-Empis, A.H. Majdalani, C. Maluk, J.L. Torero. \textbf{\enquote{Ventilation effects on the thermal characteristics of fire spread modes in open-plan compartment fires}}. 13\textsuperscript{th} International Symposium on Fire Safety Science. Waterloo, Canada. April 26--May 1.
    	
    	\item[2021] \tab *\textbf{V. Gupta}, A.F. Osorio, J.L. Torero, J.P. Hidalgo. \textbf{\enquote{Mechanisms of flame spread and burnout in large enclosure fires}}. 38\textsuperscript{th} International Symposium on Combustion. Adelaide, Australia. January 24--29.
    	
        \item[2019] \tab *\textbf{V. Gupta}, J.L. Torero, C. Maluk, J.P. Hidalgo. \textbf{\enquote{Analysis of convective heat losses in a full-scale compartment fire experiment}}. 9\textsuperscript{th} International Seminar on Fire and Explosion Hazards. St Petersburg, Russia. April 21--26.
        
        \item[2018] \tab \textbf{V. Gupta}, J.E. Cadena, J.P. Hidalgo, A.F. Osorio, C. Maluk, A.H. Majdalani. \textbf{\enquote{Accounting for uncertainty in computational fluid dynamics modelling of fully-developed compartment fires}}. 12\textsuperscript{th} International Performance-Based Codes and Fire Safety Design Methods Conference. Honolulu, USA. April 23--28.

	 \end{tablist}

    \section*{HDR Supervision}

	\begin{tablist}

		\item[2025--27] \tab Braden Southern, \textbf{\enquote{Combustion physics in energy storage systems}} (MASc). University of Waterloo. \textbf{Main supervisor}.

		\item[2025--27] \tab Keon Senez, \textbf{\enquote{Fire risk assessment framework for mass timber buildings}} (MASc). University of Waterloo. \textbf{Associate supervisor}.

		\item[2023--25] \tab Jan Dabrowski, \textbf{\enquote{Mass timber compartment fire dynamics in under-ventilated conditions}} (MASc). University of Waterloo. \textbf{Associate supervisor}.

		\item[2023--25] \tab Ayaan Lakhani, \textbf{\enquote{Gas emissions from wildland fuels}} (MASc). University of Waterloo. \textbf{Associate supervisor}.

		\item[2021--24] \tab Tony Xiao, \textbf{\enquote{Investigations of fire dynamics and enhanced fire suppression}} (PhD). The University of Sydney. \textbf{Associate supervisor}.
        
	\end{tablist}

    \section*{Media and Public Engagement} % add media appearances from August 2024 & news articles

    \subsection*{Radio}
        
        \begin{tablist}
        
        \item[2025] \tab Interview on The Mike Farwell Show (570AM), Rogers TV, and CityNews Kitchener on Canadian response to wildfires (August 2025).
        \item[2025]  \tab Interviews on Canadian Broadcasting Corporation (CBC) radio affiliates (CBC Windsor, CBC Toronto, CBC London, CBC Thunder Bay, CBC Sudbury, CBC Kitchener, and Ontario Morning) on fireproofing of communities for wildfires (August 2025).
        
        \end{tablist}

    \subsection*{News Coverage}

    \begin{tablist}
    
    \item[2025] \tab "\href{https://www.cbc.ca/news/canada/toronto/kawartha-lakes-fourth-fire-active-1.7606768}{New fire blazes out of control in Kawawrtha Lakes}", Arrthy Thayaparan, Julia Alevato. CBC News, 12th August 2025.

    \item[2025] \tab "\href{https://www.therecord.com/news/waterloo-region/university-of-waterloo-researchers-look-for-new-ways-to-fight-wildfires/article_3c6d2d6a-f8e3-54ce-8e4d-4c2df5c76241.html}{University of Waterloo researchers look for new ways to fight wildfires}", Joe McGinty. Waterloo Region Record, 14th August 2025.

    \item[2025] \tab "\href{https://educationnewscanada.com/article/education/level/university/1/1153676/wildfires-are-changing-and-so-must-our-response.html}{Wildfires are changing and so must our response}. Education News Canada, 11th August 2025. 
    
    \end{tablist}
    
\end{document}

